A subjective Bayesian framework for synthesizing deep uncertainties in climate risk management

### 2022-07-05 papers/earths-future/submission.tex
for preprint
final word edits

% Authors are individuals who have significantly contributed to the
% research and preparation of the article. Group authors are allowed, if
% each author in the group is separately identified in an appendix.)

% List authors by first name or initial followed by last name and
% separated by commas. Use \affil{} to number affiliations, and
% \thanks{} for author notes.
% Additional author notes should be indicated with \thanks{} (for
% example, for current addresses).

% Example: \authors{A. B. Author\affil{1}\thanks{Current address, Antartica}, B. C. Author\affil{2,3}, and D. E.
% Author\affil{3,4}\thanks{Also funded by Monsanto.}}

@@

%% Keypoints, final entry on title page.

%  List up to three key points (at least one is required)
%  Key Points summarize the main points and conclusions of the article
%  Each must be 140 characters or fewer with no special characters or punctuation and must be complete sentences

% Example:
% \begin{keypoints}
% \item	List up to three key points (at least one is required)
% \item	Key Points summarize the main points and conclusions of the article
% \item	Each must be 140 characters or fewer with no special characters or punctuation and must be complete sentences
% \end{keypoints}

@@

All code, including source code, is available under the GNU Public License (version 3) at \url{https://github.com/jdossgollin/2022-elevation-robustness}.
This code is written in the open source Julia programming language and detailed instructions for reproducing our results are provided.
A permanent, citeable archive of the precise version of the codes used in this study is also available on Zenodo at TBD.\footnote{Will create Zenodo release} % TODO: create Zenodo release!

>>>>

@@

@@

All code, including source code, is available under the GNU Public License (version 3) at \url{https://github.com/jdossgollin/2022-elevation-robustness}.
This code is written in the open source Julia programming language and detailed instructions for reproducing our results are provided.
A permanent, citeable archive of the precise version of the codes used in this study is also available on Zenodo at \url{https://doi.org/10.5281/zenodo.6799457}. % Update as needed
